\section*{Implementation Plan}

For the November 15 milestone, we plan to:

\begin{enumerate}

\item {\bf Validate our architecture.} Assemble all the components of our
system, and make sure there are no surprises (insufficient radio range,
insufficient on-board compute power, difficulties controlling the autopilot
from software, etc).

\item {\bf Characterize our sensing error.} Make the drone land autonomously
based on its internal pose estimate (GPS, IMU, barometer). Characterize the
error in terms of displacement from the desired landing location on the ground,
and the altitude at which the motors are powered off. This gives us a baseline
that we are trying to improve upon by adding vision.

\item {\bf Outline our vision approach.} Review the literature on vision-based
autonomous landing, and choose an approach to implement. Build a prototype
landing station with markers.

\end{enumerate}

\noindent
For the approx. December 7 deadline, we plan to:

\begin{enumerate}
\setcounter{enumi}{3}

\item {\bf Implement vision-based pose estimation.} Write the code that locates
the landing station and estimates the drone's pose with respect to it. Test
this in a lab setting, where we control the camera's position manually.

\item {\bf Couple pose estimation and control.} Make the drone land
autonomously based on real-time vision-based pose estimates. Characterize the
error as before. If our project is successful, this should improve
significantly over the vision-less baseline.

\end{enumerate}
